X\texorpdfstring{\textsuperscript{2}}-Toon: An Extended X-Toon Shader

### 2013-04-11 paper/paper.tex
Fixing compile error and fleshing out intro

\documentclass[annual]{acmsiggraph}
\usepackage{wrapfig}
\title{X\textsuperscript{2}-Toon: An Extended X-Toon Shader}

@@

\section{Introduction}

We first developed a standard cel shader using ~\cite{CelShadingTut} as a basic example.

We used the GUI framework for XNA from ~\cite{Ruminate}.

\section{Tone Detail}
\begin{wrapfigure}{r}{0.1\textwidth}
  \vspace{-20pt}
  \begin{center}
    \includegraphics[width=0.1\textwidth]{images/xtoon_skin}
  \end{center}
  \caption{2D Texture.}
  \vspace{-10pt}
  \label{fig:2dtexture}
\end{wrapfigure}
We extend the concept of a regular toon shader by adding a second dimension to the texture. While the x-axis remains as $N\cdot L$, where {\it{N}} is the surface normal and {\it{L}} is the light direction, the y-axis represents the level of detail. The higher up on the axis, the less detail is used. Conversely, the lower the y-axis value, the more detail. An example of a 2D texture used in this application can be seen in Figure~\ref{fig:2dtexture}.

@@

\section{Extensions to original X-Toon shader}
We have extended the original shader offered in the X-Toon paper to increase the usability for various new effects. The first extension involves using colours from the original model's textures when calculating the final detail. The second extension allows for the use of transparency in both the tone texture and original model's textures to create

@@

\section{Results}

@@

\section{Discussion and Future Work}

@@

\section{Conclusion}

>>>>

\documentclass[annual]{acmsiggraph}
\usepackage{wrapfig}
\usepackage{hyperref}
\title{X\texorpdfstring{\textsuperscript{2}}-Toon: An Extended X-Toon Shader}

@@

\section{Introduction}
~\cite{BTM06a} extended the classical understanding of how to perform toon shading. A new dimension of tone detail can be used to create a desired level of abstraction. Our approach implements this technique, as well as extends it. We first developed a standard cel shader using ~\cite{CelShadingTut} as a starting point. Using models downloaded from ~\cite{TurboSquid} and (*\textbf{where did we download the dude and axes??}), we used a threshold of the dot product of the lighting vector and the surface normal to produce classic toon shading. An example can be seen in Figure~\ref{fig:toonshade}.

\begin{figure}[h]
	\centering
	\includegraphics[width=1.5in]{images/classic_cel2}
	\caption{Classic Toon Shading}
	\label{fig:toonshade}
\end{figure}

A brief explanation of X-Toon is described in Section~\ref{sec:tonedetail}, our extensions in Section~\ref{sec:extensions}, and the results in Section~\ref{sec:results}. Discussion and future work are described in Section~\ref{sec:discussion} and finally the conclusion in Section~\ref{sec:conclusion}.

To make our program more interactive, we developed a GUI using the XNA GUI framework from ~\cite{Ruminate}. The controls allows the user to modify the parameters and enabled/disable features.

\section{Tone Detail}
\label{sec:tonedetail}
\begin{wrapfigure}{r}{0.1\textwidth}
  \vspace{-20pt}
  \begin{center}
    \includegraphics[width=0.1\textwidth]{images/xtoon_skin}
  \end{center}
  \caption{2D Texture.}
  \vspace{-10pt}
  \label{fig:2dtexture}
\end{wrapfigure}
We extend the concept of a regular toon shader by adding a second dimension to the texture. While the x-axis remains as $N\cdot L$, where {\it{N}} is the surface normal and {\it{L}} is the light direction, the y-axis represents the level of detail. The higher up on the axis, the less detail is used. Conversely, the lower the y-axis value, the more detail. An example of a 2D texture used in this application can be seen in Figure~\ref{fig:2dtexture}.

@@

\section{Extensions to original X-Toon shader}
\label{sec:extensions}
We have extended the original shader offered in the X-Toon paper to increase the usability for various new effects. The first extension involves using colours from the original model's textures when calculating the final detail. The second extension allows for the use of transparency in both the tone texture and original model's textures to create

@@

\section{Results}
\label{sec:results}

@@

\section{Discussion and Future Work}
\label{sec:discussion}

@@

\section{Conclusion}
\label{sec:conclusion}
